First Exclusive Measurement of Deep Virtual Compton Scattering off $^4$He: Toward the 3D tomography of nuclei

### 2017-01-21 eg6-letters/DVCS-coh-He4/dvcs_he4_prl.tex
more writing in the dvcs selection part

A DVCS process on a nuclear target differ from single nucleon scattering in 
providing access to the measure two DVCS channels. In the coherent DVCS 
channel, the target nucleus remains intact and recoils as a whole while 
emitting a real photon ($eA \rightarrow e' A' \gamma$), allowing to measure the 
nuclear GPDs of the target. In the incoherent channel, the nucleus breaks up 
and the DVCS takes place on a bound nucleon that emits the final photon ($eA 
\rightarrow e' N' \gamma$ X), enabling the GPDs measurement of the bound 
nucleons and to study the medium modifications of the nucleons in the nuclear 
medium via the GPDs.  Figure \ref{fig:diags} illustrates the dominant mechanism 
for the coherent DVCS channel on $^4$He. At sufficiently large squared electron 
momentum transfer $Q^2$ ($= -(k-k')^{2}$) and small squared momentum transfer 
$t$ ($= (p-p')^{2}$), the QCD factorization theorem predicts that the DVCS 
handbag diagram can be factorized into two parts, hard and soft parts 
\cite{Freund_Collins,Ji_Osborne}. The hard part includes photons-quark 
interaction and it is calculable through perturbative methods, while the 
soft/non-perturbative part is parametrized in terms of GPDs, which embed the 
partonic structure of the hadron.

@@

At 6 GeV incident electron beam energy, the recoil $^4$He nuclei, from the 
coherent DVCS channel, have an average momentum (per charge) around 125 MeV/c, 
while the CLAS spectrometer detects charged particles with a threshold of 250 
MeV/c. In order to ensure the exclusivity of the our coherent DVCS channel, we 
built a small and light radial time projection chamber (RTPC) to detect 
recoiling nuclei down to energies of few MeVs. Figure~\ref{fig:RTPC} presents 
our cylindrical RTPC, which is 20 cm long and 15 cm diameter, surrounding the 
$^4$He gaseous target, with a 3 cm radial drift length. The detector was 
specifically calibrated for $^4$He nuclei using elastic scattering produced 
with a 1.2~GeV electron beam.

@@

%asymmetries 
\begin{figure}[tb]
\includegraphics[width=8.9cm]{figs/coherent-ALU.pdf}
\caption{The coherent $A_{LU}$ as a function of $\phi$ in
   $Q^{2}$(top panel), $x_{B}$ (middle panel), and $-t$ (bottom panel) bins.  
   The error bars represent the statistical and the systematic uncertainties 
   added quadratically, shown on top in green are error bars representing only 
   the statistical uncertainties. The brown bands represent the systematic
uncertainties, including the normalisation systematic uncertainties. The red
curves represent fits in the form of equation \ref{eq:A_LU-coh}.}
\label{fig:alu}
\end{figure}

>>>>

A DVCS process on a nuclear target differ from single nucleon scattering in 
providing access to the measure two DVCS channels. In the coherent DVCS 
channel, the target nucleus ($A$) remains intact and recoils as a whole while 
emitting a real photon ($eA \rightarrow e' A' \gamma$), allowing to measure the 
nuclear GPDs of the target. In the incoherent channel, the nucleus breaks up 
and the DVCS takes place on a bound nucleon ($N$) that emits the final photon 
($eA \rightarrow e' N' \gamma$ X), enabling the GPDs measurement of the bound 
nucleons and to study the medium modifications of the nucleons in the nuclear 
medium via the GPDs.  Figure \ref{fig:diags} illustrates the dominant mechanism 
for the coherent DVCS channel on $^4$He. At sufficiently large squared electron 
momentum transfer $Q^2$ ($= -(k-k')^{2}$) and small squared momentum transfer 
$t$ ($= (p-p')^{2}$), the QCD factorization theorem predicts that the DVCS 
handbag diagram can be factorized into two parts, hard and soft parts 
\cite{Freund_Collins,Ji_Osborne}. The hard part includes photons-quark 
interaction and it is calculable through perturbative methods, while the 
soft/non-perturbative part is parametrized in terms of GPDs, which embed the 
partonic structure of the hadron.

@@

At 6 GeV incident electron beam energy, the recoil $^4$He nuclei, from the 
coherent DVCS channel, have an average momentum (per charge) around 125 MeV/c, 
while the CLAS spectrometer detects charged particles with a threshold of 250 
MeV/c. In order to ensure the exclusivity of the our coherent DVCS channel, we 
built a small and light radial time projection chamber (RTPC) to detect 
recoiling nuclei down to energies of few MeVs. Figure~\ref{fig:RTPC} presents 
our cylindrical RTPC, which is 20 cm long and 15 cm diameter, surrounding the 
$^4$He gaseous target and being inside the available space inside the solenoid 
, with a 3 cm radial drift length. The detector was specifically calibrated for 
$^4$He nuclei using elastic scattering produced with a 1.2~GeV electron beam.

@@

\begin{figure}[tb]
\hspace{-0.45cm}
\includegraphics[width=9.0cm]{figs/Q2_xB_t_Coh.pdf}
\caption{The $Q^{2}$ as a function of $x_{B}$ (left) and the $Q^{2}$ as a 
function of $-t$ (right) for the identified coherent DVCS events after the 
exclusivity cuts.}
\label{fig:kin-coverage}
\end{figure}

%asymmetries

We identified several background contributions to the DVCS process, in 
particular accidental events and exclusive deeply virtual $\pi^0$ production 
(DV$\pi^0$P). The accidental
events where the different particles come from different events are 
suppressed by the limited phase space allowed by the exclusivity cuts. We 
estimate the accidental events to represent 4.1\% of our sample. This 
relatively large number is due to the small cross section of the DVCS. We 
evaluated this contribution by selecting events passing all our cuts but with 
particles originating from different vertices.

Another important source of background is the deeply virtual 
$\pi^0$ production (DV$\pi^0$P), which can easily be mistaken
with DVCS when one of the two photons of the $\pi^0$ decay is produced at
low energy in the laboratory frame. To estimate the importance of
this background, we developped an event generator 
that we calibrated to match our measured experimental yield of exclusive 
$pi^0$. We used this generator together 
with a GEANT3 simulation of our detection system to estimate the ratio 
of acceptance between DV$\pi^0$P where the two photons are detected and those
where only one photon is detected and would pass our 
DVCS selection cuts. This ratio obtained from simulation is then multiplied by 
the measured yield of DV$\pi^0$P events, indicating a contamination of 2 to 4\%. 
The study of systematics errors showed that the main contributions come from 
the choice of the DVCS exclusivity cuts (8\%) and the large binning size 
(5.1\%). However added quadratically, these errors sum up to 10\% which remain 
for all bins well below the statistical errors.

The beam-spin asymmetry is measurable using a polarized lepton beam on an 
unpolarized target (U). It is convenient to use the beam-spin asymmetry as a 
DVCS observable because most of the experimental normalization and acceptance 
issues cancel out in the asymmetry ratio. It is defined as in terms of the 
cross sections as:
  \begin{equation}
  A_{LU} = \frac{d^{5}\sigma^{+} - d^{5}\sigma^{-} }
                {d^{5}\sigma^{+} + d^{5}\sigma^{-}}.
    \label{BSA_equation}
  \end{equation}
  where $d^{5}\sigma^{+}$($d^{5}\sigma^{-}$) is the DVCS differential cross section for a positive (negative) beam helicity.

In terms of the collected number of events in each beam-helicity state 
($N^{+}$, $N^{-}$), A LU can be
expressed as:

\begin{equation}
A_{LU} = \frac{1}{P_{B}} \frac{N^{+} - N^{-}}{N^{+} + N^{-} }.
\end{equation}
%
where $P_{B}$ is the beam polarization, and $N^{+}$ and $N^{-}$ are the number of events detected with positive and negative electron helicity, respectively. The statistical uncertainty of $A_{LU}$ is
%
\begin{equation}
   \sigma_{A_{LU}} = \frac{1}{P_{B}} \sqrt{ \frac{1 - (P_{B}A_{LU})^{2}}{N}}
\end{equation}
%
where $N (N^{+} + N^{-}) $ is the total number of measured events.
%

\begin{figure}[tb]
\includegraphics[width=8.9cm]{figs/coherent-ALU.pdf}
\caption{The coherent $A_{LU}$ as a function of $\phi$ in
   $Q^{2}$(top panel), $x_{B}$ (middle panel), and $-t$ (bottom panel) bins.  
   The error bars represent the statistical and the systematic uncertainties 
   added quadratically, shown on top in green are error bars representing only 
   the statistical uncertainties. The brown bands represent the systematic
uncertainties, including the normalisation systematic uncertainties. The red
curves represent fits in the form of equation \ref{eq:A_LU-coh}.}
\label{fig:alu}
\end{figure}
